\documentclass[11pt,a4paper]{moderncv}

\moderncvtheme[purple]{classic}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8, top=1cm, bottom=0.5cm]{geometry}

\usepackage[unicode]{hyperref}
\usepackage{color}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}
\usepackage{fontawesome5}
\firstname{Vadim}
\familyname{Ponomarev}
\title{Intern developer}
\address{}{Saint-Petersburg, Russia}
\mobile{8-911-917-2928}
\email{vadim.v.ponomarev@gmail.com}
\social[github]{VxDxK}
\newcommand*{\telegramsocialsymbol}  {\small\faTelegram}
\RenewDocumentCommand{\social}{O{}O{}m}{%
    \ifthenelse{\equal{#2}{}}%
    {
        \ifthenelse{\equal{#1}{linkedin}}{\collectionadd[linkedin]{socials}{\protect\httplink[#3]{www.linkedin.com/in/#3}}}{}%
        \ifthenelse{\equal{#1}{twitter}} {\collectionadd[twitter]{socials} {\protect\httplink[#3]{www.twitter.com/#3}}}    {}%
        \ifthenelse{\equal{#1}{github}}  {\collectionadd[github]{socials}  {\protect\httplink[#3]{www.github.com/#3}}}     {}%
        \ifthenelse{\equal{#1}{telegram}}  {\collectionadd[telegram]{socials}  {\protect\httplink[#3]{www.t.me/#3}}}     {}%
    }
    {\collectionadd[#1]{socials}{\protect\httplink[#3]{#2}}}}
\social[telegram]{vxdxk}

% From tex.stackexchange
\renewcommand*{\cventry}[7][.25em]{%
    \cvitem[#1]{#2}{%
            {\bfseries#3}%
%   \ifthenelse{\equal{#4}{}}{}{, {\slshape#4}}% I changed this line (with comma) ...
        \ifthenelse{\equal{#4}{}}{}{ {\slshape#4}}% ... into this one (without comma).
        \ifthenelse{\equal{#5}{}}{}{ #5}%
        \ifthenelse{\equal{#6}{}}{}{ #6}%
        .\strut%
        \ifx&#7&%
        \else{\newline{}\begin{minipage}[t]{\linewidth}
                            \small#7
        \end{minipage}}\fi}}

\makeatletter
\renewcommand*{\bibliographyitemlabel}{\@biblabel{\arabic{enumiv}}}
\makeatother

\begin{document}
    \maketitle
    \section{Experience}
    \cvline
      {Room bot}
      {\url{https://github.com/VxDxK/VDK-room-bot}\newline{}
      \textbf{Bot for Discord}\newline{}
      Discord API experience.\newline}
    \cvline
      {ITMO EDU project}
      {\url{https://github.com/VxDxK/programming-group-project}\newline{}
      \textbf{Project for a university competition.}\newline{}
      Group work.\newline{}
      Lead role.\newline{}
      Added CI\textbackslash CD to automize Javadoc uploading.}
    \cvline
    {UDP server and client(cli and gui)}
    {\url{https://github.com/VxDxK/ifmo-labs-1/tree/proga-lab-8}\newline{}
    \textbf{University semester work}\newline{}
    Java NIO.\newline{}
    Swing GUI.\newline{}
    Postgresql database.
    }
    \cvline
    {Ray tracer}
    {\url{https://github.com/VxDxK/ray-tracer}\newline{}
    Rendering 3D images with diffuse, metallic, dielectric spheres.\newline{}}
    \cventry
      {July 2021}
      {Summer intership}
      {ITIVITI}
      {\newline{}\url{https://www.itiviti.com/}}{}
      {Java core team.\newline{}
      Software development. Configure Maven for reproducible builds}
    \cventry
      {1 Jul 2020 - 15 Jul 2020}
      {Summer intership}
      {ITIVITI}
      {\newline{}\url{https://www.itiviti.com/}}{}
      {}

    \section{Skills}
    \cvline
    {Languages}{Java, Spring(MVC, Data, Security), SQL}
    \cvline
    {Tools}{Git, Maven, JUnit}
    \cvline
    {Experience}{Gradle, Hibernate, Jira}

    \section{Education}

    \subsection{University}
    \cventry
    {2021 - 2025}
    {Computer science, Bachelor}
    {St.Petersburg National Research University of Information Technologies, Mechanics \& Optics.}
    {\newline Faculty of Software Engineering and Computer Systems.}{\newline Program Engineer}{}
    \subsection{Courses}
    \cventry
    {2018 - 2020}
    {ITMO olympic programming school}
    {\newline Learned about algorithms, code optimization, graphs}
    {}{}{}
\end{document}